---
title: "Big Markdown Group"
author: "Dog"
date: "3/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

questions to answer
Is there a way to classify if someone smokes based on body measure, blood pressure, and cholesterol? Do certain demographics increase the percentage of smokers?
Is there a way to predict blood pressure levels based on body measures and cholesterol? Does smoking status or certain demographics impact blood pressure as well?

Do not use these variables:
dr1exmer interviewer id code


# Exploratory Data Analysis

```{r}

## first diastolic reading
hist(train_data$BPXDI1)
 
## second diastolic reading
hist(train_data$BPXDI2)


## third diastolic reading
hist(train_data$BPXDI3)

## all of the diastolic appear to be approximately normal


## first systolic reading
hist(train_data$BPXSY1)


## second systolic reading
hist(train_data$BPXSY2)


## third systolic reading
hist(train_data$BPXSY3)

## all of the systolic appear to be slightly right skewed, but mostly normal

pairs(~ BPXSY1 + BPXSY2 + BPXSY3 + BPXDI1 + BPXDI2 + BPXDI3, data = train_data)     
## systolic and diastolic are positively correlated, some outliers with low diastolic values but higher systolic values

```

```{r}

## hist of ldl cholesterol
hist(train_data$LBXTC)

## hist of total cholesterol
hist(train_data$LBDTCSI)

## both are approximately normal

pairs(~ DR1TKCAL + DR1TPROT + DR1TCARB + DR1TSUGR + DR1TFIBE, data = train_data)
## looking at this pairs plot = It appears the Kcal is positively correlated with Carb the most. Carb and the Sugr variables also appear to be positively correlated. Kcal and Prot appear to be positively correlated as well, but not as strong as the other two relationships.

pairs(~ DR1TTFAT + DR1TSFAT + DR1TMFAT + DR1TPFAT, data = train_data)
## all fat data looks to be positively correlated 
```




##  YEaaaaaaooooooo

