---
title: "Big Markdown Group"
author: "Dog"
date: "3/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Kaggle name: 

In this report, we hope to answer:

1. Can we predict total cholesterol levels (LBXTC) based on dietary cholesterol intake (DR1TCHOL), and are there other nutrients that can predict it better?

We used linear regression, polynomial regression, and lasso regression to explore this question.

2. Can we accurately classify subjects with high cholesterol based on their intake of various nutrients?

We used a neural network to explore this question. 


# Exploratory Data Analysis

```{r}

## first diastolic reading
hist(train_data$BPXDI1)
 
## second diastolic reading
hist(train_data$BPXDI2)


## third diastolic reading
hist(train_data$BPXDI3)

## all of the diastolic appear to be approximately normal


## first systolic reading
hist(train_data$BPXSY1)


## second systolic reading
hist(train_data$BPXSY2)


## third systolic reading
hist(train_data$BPXSY3)

## all of the systolic appear to be slightly right skewed, but mostly normal

pairs(~ BPXSY1 + BPXSY2 + BPXSY3 + BPXDI1 + BPXDI2 + BPXDI3, data = train_data)     
## systolic and diastolic are positively correlated, some outliers with low diastolic values but higher systolic values

```

```{r}

## hist of ldl cholesterol
hist(train_data$LBXTC)

## hist of total cholesterol
hist(train_data$LBDTCSI)

## both are approximately normal

pairs(~ DR1TKCAL + DR1TPROT + DR1TCARB + DR1TSUGR + DR1TFIBE, data = train_data)
## looking at this pairs plot = It appears the Kcal is positively correlated with Carb the most. Carb and the Sugr variables also appear to be positively correlated. Kcal and Prot appear to be positively correlated as well, but not as strong as the other two relationships.

pairs(~ DR1TTFAT + DR1TSFAT + DR1TMFAT + DR1TPFAT, data = train_data)
## all fat data looks to be positively correlated 
```




##  YEaaaaaaooooooo

