---
title: "Big Markdown Group"
author: "Dog"
date: "3/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

questions to answer
Is there a way to classify if someone smokes based on body measure, blood pressure, and cholesterol? Do certain demographics increase the percentage of smokers?
Is there a way to predict blood pressure levels based on body measures and cholesterol? Does smoking status or certain demographics impact blood pressure as well?

Do not use these variables:
dr1exmer interviewer id code


# Exploratory Data Analysis

```{r}

## first diastolic reading
hist(train_data$BPXDI1)
 
## second diastolic reading
hist(train_data$BPXDI2)


## third diastolic reading
hist(train_data$BPXDI3)



## first systolic reading
hist(train_data$BPXSY1)


## second systolic reading
hist(train_data$BPXSY2)


## third systolic reading
hist(train_data$BPXSY3)


pairs(~ BPXSY1 + BPXSY2 + BPXSY3 + BPXDI1 + BPXDI2 + BPXDI3, data = train_data)     
## systolic blood pressures more precise than diastolic blood pressures (more correlated)

```

```{r}

## hist of ldl cholesterol
hist(train_data$LBXTC)


 
```




##  YEaaaaaaooooooo

